%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Microsoft} % Organization
    {Pune, India} % Location
    {Aug. 2023 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	    \item {\textbf{Copilot Studio} product feature work.}
	    \item {Used \textbf{AzureDevOps} for project management and CICD pipelines.}
	    \item {Developed version tracking tool using Blazor UI.}
	    \item {Handling \textbf{product level Quality ownership} following SDP.}
	    \item {RAI Testing for Copilot Studio features.}
      \end{cvitems}
    }

%---------------------------------------------------------
%---------------------------------------------------------
  \cventry
    {Principal SDET} % Job title
    {Nuance Communications, Inc..} % Organization
    {Pune, India} % Location
    {Nov. 2015 - Aug. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	    \item {\textbf{Principal QA} for a Project - defining the QA strategy and approach. Involved in Planning and Design meetings with PM's.}
	    \item {Used \textbf{Cypress} for testing micro-frontends in Mix Project.}
	    \item {Developed Quality Dashboards for tracking data from different tools/Services using Flask and Python.}
	    \item {Handling \textbf{product level Quality ownership}, striving to new limits with process imporvements.}
	    \item {Training team mates and POC on different tools that can be used to improve our Quality}
		  \item {Created a framework template that can be used for further angular project automation using \textbf{Protractor}, Gulp, Cucumber and TypeScript.}
		  \item {\textbf{Evaluation} of Test Case Management \textbf{Tools} for the company level use that suites testing needs appropriately for different kinds of projects.}
      \item {\textbf{Ownership} of feature in release, following whole STLC for owned feature.}
		  \item {\textbf{OWASP} Top 10 Security Testing on ODI Web Application.}
      \item {Created a new framework for Reporting product using Selenium, \textbf{Gauge} and Java.}
      \item {Added multiple features in the framework as per the project structure. \textbf{CLI} driver for ETL automation.}
      \item {Installation and configuration of product on Unix Systems. Writing scripts to automate the installation and configuration steps.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Automation Engineer (Module Lead)} % Job title
    {Persistent Systems Ltd.} % Organization
    {Pune, India} % Location
    {Dec. 2012 - Nov. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Automation of test cases using existing frameworks.}
	  \item {\textbf{Migrated} 1.5K selenium 1.0 test cases to Selenium 2.0 \textbf{framework} worked alone}
      \item {Writing \textbf{Test Plan} and \textbf{Test Cases}. Executing test cases manually.}
       \item {Creating reusable user defined libraries.}
      \item {Reporting bugs at all stages of testing.}
     \item {Regression testing and shell scripting.}
     \item {\textbf{Managing} tasks of subordinates and reporting the plans for week.}
     \item {\textbf{Training} new joiners and planning their induction sessions from other team members.}
   \item {Maintaining frameworks of \textbf{Selenium} and \textbf{Axis2}}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Automation Test Engineer (Consultant)} % Job title
    {ZenTEST Labs} % Organization
    {Pune, India} % Location
    {Apr. 2011 - Dec. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implementing automation Framework. PHP, Java and C\# Framework implemented with \textbf{EC2 integration} for execution with \textbf{CI}.}
        \item {Creating and enhancing test scripts to increase maintainability, readability, reliability and portability.}
        \item {Creating reusable user defined libraries. Error handling and exception handling}
        \item {Debugging and reviewing scripts of Team members.}
        \item {Designing requirement based test cases.}
       \item {Writing and Executing manual test cases}
       \item {Reporting bugs at all stages of testing.}
      \item {Identifying functional issues with the application.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Tester} % Job title
    {SQS-India } % Organization
    {Pune, India} % Location
    {Jun. 2010 - Apr. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Functionality testing and finding different kinds of defects in the project.}
        \item {Uploading the defect into client’s Database (DevTrack).}
        \item {Performed Smoke, Localization, and Ad-hoc Testing}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
