%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Summary}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
\begin{cvitemize}
 \item {A Decade of hands-on experience in successfully implementing numerous software automation and performance testing solutions, using both vendor-based and open source technologies.}
 \item {Expertise of Agile Testing, \textbf{Web UI} and \textbf{Web Services} Automation with \textbf{10+ years exp}.}
 \item {Training and Guiding team members with Product understanding and Motivating for new Learnings.}
 \item {Selenium used with \textbf{PHP, Java, C\#.net, Python, TypeScript} and developed frame work for each. \textbf{CI} with EC2 instances for execution.}
 
 \item {Expertise \textbf{CI} handling for dev and QA Pipelines with Jenkins and \textbf{Gitlab CI, Github Actions, Circle CI}}.
 
 \item {Expertise \textbf{CD} using tools like \textbf{K8S, Docker, Harness, Helm, Racher}}

 \item {Created Framework \textbf{SeUnit,NuanceDriver} Using Selenium Web driver and Java (BDD).}
 
 \item {A good insight on evaluating tools and technologies to be used as per the requirements}
 
 \item {Hands on experience in testing micro frontends using \textbf{Cypress}. Intregrated with \textbf{Coverage, ReportPortal, Applitools, qTest}} 

 \item {\textbf{Migration} of existing framework from RC to Webdriver without any rework on 1.5k testcases}

 \item {Using \textbf{Gauge} framework and tweaking to work with \textbf{CLIFramework} using jSch as per the need of the framework.}

 \item {Hands-on of \textbf{Sahi \& VSTS} Automation Tool and \textbf{Linux/Shell} scripting.}

 \item {Worked on AI Based Application (NLP, Speech Recognition and TTS), corporate banking, email marketing and analytics application.}

 \item {\textbf{OWASP} Testing using ZAP tools}

 \item {Highly organized, versatile and results-oriented team player with an energetic and articulate approach to testing. \textbf{Quick learner}, good communication skills, interpersonal skills, \textbf{leadership skills}.}

 \item {Have strong \textbf{problem solving} capabilities and \textbf{analytical} skills.}

 \item {\textbf{Handled Team} of 5-10 for \textbf{7 years} persons with their tasks and planning.}
 
 \item {\textbf{Leading} as QA to a new \textbf{project} at Nuance, automation done with \textbf{Cypress,Taiko,Protractor} in TypeScript/Javascript. Execution with Selenium \textbf{Dockers}.}
\end{cvitemize}
\end{cventries}
